Title

### 2022-07-07 journal/reviewer-response/JOURNALID-RX.tex
new reviewer response upgrade

%@TheDoctorRAB
%standard white paper/preproposal format
%
%%%%%
%
%REFERENCES
%
%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
%nsf.bst - numbered citations in order of appearance, full author list in references section
%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
%ans.bst is for ANS only. 
%
%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
%bst renders the author list itself
%
%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
%
%title = {{}} for all
%
%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
%standard.bst \cite{-} - Borrelli (2021) in the text
%standard.bst lists references alphabetically
%the rest list numerically
%
%%%%%
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
\usepackage{float}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level

@@

\usepackage[singlelinecheck=false,labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup[table]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format

@@

\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
\SetWatermarkScale{0.20}

%\usepackage{xr} %for revisions - will cross reference from one file to here
%\externaldocument{/path/to/auxfilename} %aux file needed

%%%%% toc and glossaries
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
\usepackage{titlesec,titletoc}
%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through
%\titleformat{\part}{\normalfont\Large\bfseries\filcenter}{\thepart}{}{}[]
%\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}
%\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
%\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}
%\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
%\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}
\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}
\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}

@@

%%%%% header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize Manuscript ID - Load following}
\chead{\scriptsize \textit{First Author et al. - Draft Manuscript}}
\rhead{\scriptsize \today}
\rfoot{\thepage}
%%%%%

\begin{filecontents}{references.bib} 
    @misc{
        hun19a,
        author = {Hunton, Paul J. and England, Robert T.},
        title = {{Addressing nuclear I\&C modernization through application of techniques employed in other industries}},
        year = {2019},
        note = {{INL/EXT-19-55799}}
    }
    @conference{
        las18a,
        author = {Lassell, S. A. and Hawari, A. I. and Benjamin, J. S. and Barnes, K. T. and Wright, V. L.},
        title = {{Methodology development for cybersecurity robustness and vulnerability assessment of university research reactors}},
        year = { 2018},
        organization = {Proc., American Nuclear Society Annual Meeting },
        address = {Philadelphia, Pennsylvania}
    }
    @article{
        mac19a,
        author = {MacLean, Trevor and Borrelli, Robert and Haney, Michael},
        title = {{Cybersecurity modeling of non-critical nuclear power plant digital instrumentation}},
        journal = {{Critical Infrastructure Protection XIII, J. Staggs, S. Shenoi, eds.}},
        volume = {{Chapter 5}},
        year = {2019},
        pages = {86}
    }
    @incollection{
        mil17a,
        author = {Miller, Steven E.},
        title = {{Cyber Threats, Nuclear Analogies? Divergent Trajectories in Adapting to New Dual-Use Technologies}},
        booktitle = {Understanding Cyber Conflict: 14 Analogies},
        publisher = {Georgetown University Press},
        year = {2017},
        editor = {Perkovich, George and Levite, Ariel E.},
        pages = {161}
    }
    @book{
        ost19a,
        author = {Ostrom, Lee T. and Wilhelmsen, Cheryl A.},
        title = {{Risk assessment: Tools, techniques, and their applications}},
        publisher = {John Wiley \& Sons, Inc.},
        isbn = {978-1119483465},
        year = {2019}
    }
\end{filecontents}

%%%%% acronyms
% alphabetical ordering is automated
\newacronym{nrs}{NRHES}{Nuclear Renewable Hybrid Energy System}
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{ci}{CI}{Consistency Index}
\newacronym{cr}{CR}{Consistency Ratio}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{lwr}{LWR}{Light Water Reactor}
\newacronym{eia}{EIA}{U.S. Energy Information Administration}
\newacronym{oer}{OER}{Online Educational Resource}
\newacronym{lms}{LMS}{Learning Management System}
\newacronym{cps}{CPS}{Cyber-Physical Systems}
\newacronym{nsf}{NSF}{National Science Foundation}
\newacronym{wsc}{WSC}{Western Services Corporation}
\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
\newacronym{pwr}{PWR}{Pressurized Water Reactor}
\newacronym{roi}{ROI}{Return on Investment}
\newacronym{ic}{I\&C}{Instrumentation \& Controls}
\newacronym{mwe}{MWe}{Megawatts-electric}
\newacronym{ics}{ICS}{Industrial Control Systems}
\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
\newacronym{ip}{IP}{Internet Protocol}
\newacronym{udp}{UDP}{User Datagram Protocol}
\newacronym{tva}{TVA}{Tennessee Valley Authority}
\newacronym{plc}{PLC}{Programmable Logic Controller}
\newacronym{vfd}{VFD}{Variable Frequency Drive}
\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
\newacronym{onl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{mim}{MITM}{Man in the Middle}
\newacronym{dos}{DDoS}{Distributed Denial of Service}
\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
\newacronym{cs}{CS}{Critical System}
\newacronym{loc}{LOCA}{Loss of Coolant Accident}
\newacronym{hmi}{HMI}{Human Machine Interface}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{bol}{BOL}{beginning-of-life}
\newacronym{eol}{EOL}{end-of-life}
\newacronym{mol}{MOL}{middle-of-life}
\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
\newacronym{ccc}{CCC}{Computing Community Consortium}
\newacronym{neu}{NEUP}{Nuclear Energy University Program}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{nei}{NEI}{Nuclear Energy Institute}
\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
%\newacronym{}{}{}
%%%%%

@@

\begin{titlepage}
    \title{Title}
    \author{
        First, 
        Second,
        \textsuperscript{*}Third
        \\ \\ \\
        Affiliation 1\\
        Affiliation 2\\
        Affilation 3
        \\ \\ \\
        \textsuperscript{*}email
    }
\clearpage %not have page number on title page
\maketitle
\vspace*{\fill}
\begin{flushright}{
        \noindent Number of pages - \pageref{LastPage} \\
        \noindent Number of tables - \totaltables \\
        \noindent Number of figures - \totalfigures 
}
\end{flushright}
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

%spacing options
\onehalfspacing %linespacing
%\setstretch{1.05} %linespacing
%\spacing{1.25} %equivalent to 1.5 line spacing in Word

%linenumbering
\linenumbers %toggle line numbers
\pagewiselinenumbers %reset line numbers on new page
\modulolinenumbers[1] %line numbering interval

\section*{Abstract}

@@

\printnoidxglossary

\section{Introduction} \label{sec-intro}

\subsection{Motivation} \label{sec-motiv}

\subsection{Goals} \label{sec-goals}
We ask the following questions - 
\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
    \item 1 
    \item 2
    \item 3
\end{enumerate}

To address these, we have the following goals for this paper - 
\begin{enumerate}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*,label=(\arabic*)]
    \item a
    \item b
    \item c
\end{enumerate}

\section{Background} \label{sec-bak}

\section{Theory} \label{sec-theo}

\section{Methodology} \label{sec-meth}

\section{Results} \label{sec-res}
\subsection{Objective} \label{sec-obj}

\section{Discussion} \label{sec-disc}

\section{Future work} \label{sec-fwk}

\section{Summary remarks} \label{sec-sum}

Major results and implications include - 
\begin{itemize}[topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item 1
    \item 2
    \item 3
\end{itemize}

\section*{Acknowledgements}

\bibliographystyle{standard}
\setlength{\bibhang}{0pt}
\bibliography{references}

\section*{Tables}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\tablename~\oldnumberline}%
\listoftables%
}

%\begin{spacing}{1}
%\begin{longtable}{|c|c|c|c|c|}
%    \caption{Title}
%    \label{tab-label-name} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endfirsthead
%    \multicolumn{5}{c}{{\tablename\ \thetable{} - continued}} \\
%    \hline
%    \multicolumn{1}{|c|}{A}&
%    \multicolumn{1}{c|}{B}&
%    \multicolumn{1}{c|}{C}&
%    \multicolumn{1}{c|}{D}&
%    \multicolumn{1}{c|}{E}
%    \\
%    \hline
%    \endhead
%    \hline
%    \endfoot
%    \hline
%    \endlastfoot
%    X
%    &X
%    &X
%    &X
%    &X
%    \\
%    \hline
%\end{longtable}
%\end{spacing}

\section*{Figures}

{%
\let\oldnumberline\numberline%
\renewcommand{\numberline}{\figurename~\oldnumberline}%
\listoffigures%
}

%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=0.X\textwidth]{.png}
%    \caption{}
%    \label{fig-label-name}
%\end{figure}

\begin{appendices}

    \renewcommand{\thesection}{\Roman{section}}
    \titleformat{\section}{\normalfont\large\bfseries\filcenter}{Appendix \thesection:}{1ex}{}[]

\section{Title}\label{app-}

\end{appendices}

>>>>

%@TheDoctorRAB
%standard white paper/preproposal format
%
%%%%%
%
%REFERENCES
%
%neup.bst - numbered citations in order of appearance, short author list with et al in reference section
%nsf.bst - numbered citations in order of appearance, full author list in references section
%standard.bst - citations with author last name with et al for more than 2 authors; full author list in references section
%ans.bst is for ANS only. 
%
%author = {Lastname, Firstname and Lastname, Firstname and Lastname, Firstname} for all bst formats
%bst renders the author list itself
%
%author = {{Nuclear Regulatory Commission}} if the author is an organization, institution, etc., and not people
%
%title = {{}} for all
%
%for all - use \citep{-} - [1] or (Borrelli, 2021) in the text
%standard.bst \cite{-} - Borrelli (2021) in the text
%standard.bst lists references alphabetically
%the rest list numerically
%
%%%%%
\documentclass[11pt,a4paper]{article}
\usepackage[lmargin=1in,rmargin=1in,tmargin=1in,bmargin=1in]{geometry}
\usepackage[pagewise]{lineno} %line numbering
\usepackage{setspace}
\usepackage{ulem} %strikethrough - do not \sout{\cite{}}
\usepackage[pdftex,dvipsnames]{xcolor,colortbl} %change font color
\usepackage{graphicx}
\usepackage{filecontents}
\usepackage{tablefootnote}
\usepackage{footnotehyper}
\usepackage{float}
%\usepackage{subfig}
\usepackage[yyyymmdd]{datetime} %date format
\renewcommand{\dateseparator}{.}
\graphicspath{{../img/}} %path to graphics
\setcounter{secnumdepth}{5} %set subsection to nth level
%\usepackage{mypythonhighlight}
%\usepackage{lipsum}

@@

\usepackage[singlelinecheck=false,labelfont=bf]{caption}
\usepackage{subcaption}
\captionsetup[table]{justification=centering,skip=7pt,labelformat={default},labelsep=period,name={Table}} %sets a space after table caption
\captionsetup[figure]{justification=justified,skip=7pt,labelformat={default},labelsep=period,name={Figure}} %sets space above caption, 'figure' format

@@

%\usepackage[firstpage,vpos=0.67\paperheight]{draftwatermark}
%\SetWatermarkText{\shortstack{DRAFT\\do not distribute}}
%\SetWatermarkScale{0.20}

%to crossref between files
%clear both directories
%pdflatex manuscript first
%pdflatex this file next
%manuscript needs correponding code here with /path/to/this-file
\usepackage{xr}
\externaldocument{/path/to/manuscript} %crossref through aux file

\makeatletter %make text labels
\newcommand{\labeltext}[3][]{%
    \@bsphack%
    \csname phantomsection\endcsname %in case hyperref is used
    \def\tst{#1}%
    \def\labelmarkup{} %how to markup the label itself
    %\def\refmarkup{\labelmarkup} %How to markup the reference
    \def\refmarkup{}%
    \ifx\tst\empty\def\@currentlabel{\refmarkup{#2}}{\label{#3}}%
    \else\def\@currentlabel{\refmarkup{#1}}{\label{#3}}\fi%
    \@esphack%
    \labelmarkup{#2}% visible printed text.
}

%%%%% toc and glossaries
\usepackage[acronym,nomain,nonumberlist]{glossaries}
\makenoidxglossaries
\usepackage{titlesec,titletoc}
%\renewcommand{\thepart}{ARTICLE \Roman{part}} %puts the label into the command so \thelabel will carry through
%\renewcommand{\thesection}{\arabic{section}} %puts the label into the command so \thelabel will carry through

\titleformat{\part}{\normalfont\large\bfseries\filcenter}{\thepart}{}{}[]
\titlespacing\part{0pt}{0.75\baselineskip}{0.50\baselineskip}

\titleformat{\section}[runin]{\normalfont\large\bfseries}{\thesection}{-1em}{}[.]
\titlespacing*\section{0pt}{0.55\baselineskip}{0.35\baselineskip}

\titleformat{\subsection}[runin]{\normalfont\normalsize\bfseries}{\thesubsection}{-1em}{}[.]
\titlespacing*\subsection{0pt}{0.45\baselineskip}{0.30\baselineskip}

\titleformat{\paragraph}[runin]{\normalfont\normalsize\bfseries\itshape}{\theparagraph}{-1em}{}[.]
\titlespacing*\paragraph{0pt}{0.40\baselineskip}{0.25\baselineskip}

%\titleformat{\paragraph}[hang]{\normalfont\normalsize\bfseries}{\theparagraph}{5pt}{}[]
%\titlespacing*\paragraph{0pt}{0.50\baselineskip}{0.25\baselineskip}

\titleformat{\subparagraph}[runin]{\normalfont\normalsize\itshape}{\thesubparagraph}{-1em}{}[.]
\titlespacing*\subparagraph{0pt}{0.40\baselineskip}{0.20\baselineskip}

@@

%%%%% header and footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{} %move page number to bottom right
%\renewcommand{\headrulewidth}{0pt} %set line thickness in header; uncomment as is to remove line
\lhead{\scriptsize JOURNAL-ID}
\chead{\scriptsize \textit{Author et al.} - Reviewer X}
\rhead{\scriptsize \today}
\rfoot{\thepage} %move page number to bottom right
%%%%%

\begin{filecontents}{references.bib} 
\end{filecontents}

%%%%% acronyms
%\newacronym{}{}{}
%%%%%

@@

\begin{titlepage}
    \title{Title}
    \author{
        Author 1, 
        Author 2, 
        \textsuperscript{*}Author 3
        \\ \\ \\
        Affiliation
        \\ \\ \\
        \textsuperscript{*}rborrelli@uidaho.edu
        \\ \\ \\ 
        Response to Reviewer
    }
\clearpage %not have page number on title page
\maketitle
\thispagestyle{empty} %start with page number 1 on second page
\end{titlepage}

\part*{Reviewer X}

\noindent Thank you for the peer review of this manuscript. Each comment was considered carefully. The manuscript has been revised accordingly in the hope that the updated paper is worthy of publication. A detailed response to each comment is provided in this document.

\section*{General comments}
\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
    \item Comment
\end{enumerate}

\subsection*{Response}
Response

\paragraph*{Revisions}
Revisions
\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
    \item\labeltext{Statement.}{1-label}
\end{enumerate}

\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
    \item Comment
\end{enumerate}

\subsection*{Response}
Response

\paragraph*{Revisions}
Revisions
\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
    \item\labeltext{Statement.}{1-label-2}
\end{enumerate}

@@

\section*{Editorial comments}
\begin{enumerate}[series=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
\end{enumerate}

\subsection*{Response}
\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
    \item Reply
\end{enumerate}

\begin{enumerate}[resume=innerlist,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),align=left,leftmargin=*]
    \item Abstract 1 - \labeltext{`...essential components \textit{to} back-end...' $\rightarrow$ `...essential components \textit{of} back-end...'}{1-ed1}
\end{enumerate}

\subsection*{Response}
\begin{enumerate}[leftmargin=.5in,rightmargin=.5in,topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex,label=(\roman*)]
    \item Reply
\end{enumerate}

%\newpage

%\part*{References}
%\bibliographystyle{nsf}
%\setlength{\bibhang}{0pt}
%\bibliography{references}
